Discriminative Sensing Based on Signal Processing

### 2017-10-25 docs/thesis/chapters/appendix/b_pca_svm_cfa/pca_svm_cfa.tex
pca_rfe conclusion

We propose a critical factors analysis based on Principal Compoment Analytis (PCA) for visual discriminant analysis and based on RFE combined with Support Vector Machine (SVM) \cite{hearst1998support}, applied to the survey that evaluates the IT governance of brazilian public organizations, in order to identify the CSF for IT governance of the public sector according to TCU. Results show how PCA can make the data discriminative and that SVM is the classifier that best performs and obtains an accuracy of 91.42\% to learn and classify according to TCU's IT governance evaluation of brazilian public sector. Finally, SVM is used to highlight the more significant features identified by RFE, wich are limilar to CSFs previsously identified by a qualitative analysis of the same datased.

@@

pca make possible visual discriminative analysis of reduced dataset but it is not easy make correlation betwee extracted features and its original, therefore it is necessary adictional techniques to identify CSF.

SVM have been shown to generalize well even for small sample classification[8]. SVM presents high performance to reproduce the iGovTI classification and can be used for RFE in order to identify CSF

The selected features revealed by RFE are quite similar to the qualitative analysis of Ramos \emph{et al} \cite{ramos2016information}.

Question with low variance can indicate that it is irrelevant for evaluation, since its value is almost the same all the time

>>>>

We propose a critical factors analysis based on Principal Compoment Analytis (PCA) for visual discriminant analysis and based on RFE combined with Support Vector Machine (SVM) \cite{hearst1998support}, applied to the survey that evaluates the IT governance of brazilian public organizations, in order to identify the CSF for IT governance of the public sector according to TCU. Results show how PCA can make the data discriminative and that SVM is the classifier that best performs and obtains an accuracy of 91.42\% to learn and classify according to TCU's IT governance evaluation of brazilian public sector. Finally, SVM is used to highlight the more significant features identified by RFE, wich are similar to CSFs previsously identified by a qualitative analysis of the same datased.

@@

The proposed approach is evaluated and the experimental results show that the visual discriminant analysis, throught PCA, highlights important characteristcs of the data, and that a selected classifier and RFE can be applied for iGovTI classification and for CSF identification.

Results show how PCA can make the data discriminative, however it is hard to identify what original variables are most relevant. Therefore, it is still necessary an additional method to reveal what are the CSF for iGovTI. For this problem, we propose a CSF analysis based on RFE. Since RFE depends on a classifier to select the most relevant features, we perform an algorithm evaluation to identify the classifier with the highest performance, and results show that SVM \cite{hearst1998support} presents the best accuracy, with 91.42\%.

Finally, SVM is used to select the more significant features identified by RFE, wich are 69,9\% similar to CSFs previsously identified by a qualitative analysis of the same datased.
